Variation on a Variational Principle

### 2020-09-20 draft1.tex
adding figures

\newcommand{\thmref}[1]{Theorem \ref{#1}}
\newcommand{\prpref}[1]{Proposition \ref{#1}}
\newcommand{\lemref}[1]{Lemma \ref{#1}}
\newcommand{\comment}[1]{}

@@

Suppose the edges are labelled $e_i$,
which goes between vertices $v_i$ and $v_{i+1}$,
and suppose $e_i$ is assigned dihedral angle $\alpha_i$.
Let $e'$ be a new edge addeed to the base face of $P_n$
such that it separates the base face into a triangle and
an $(n-1)$-gon;
suppose the sides of the triangle are
$e_i, e_{i+1}$, and $e'$.
The new face corresponding to $e'$ separates $P_n$ into
an ideal tetrahedron $T$ and an ideal pyramid $P_{n-1}$.
We assign the dihedral angle of $\pi - \alpha_i - \alpha_{i+1}$
to $e'$ in $T$, and assign $\alpha_i + \alpha_{i+1}$ to $e'$ in $P_{n-1}$.
Clearly the condition that the sum of dihedral angles are satisfied
in $T$ and $P_{n-1}$.
It remains to check that the dihedral angles assigned to the vertical edges
are correct.
For the vertical edge associated $v_j$ for $j \neq i, i+2$,
there is nothing to check;
for $j = i$, the dihedral angles are
$\pi - \alpha_i - (\pi - \alpha_i - \alpha_{i-1})$
in $T$ and $\pi - \alpha_{i-1} - (\alpha_i + \alpha_{i+1})$ in $P_{n-1}$,
which sum to $\pi - \alpha_i - \alpha_{i+1}$;
it is similar for $j = i+2$.

See Figure \ref{TODO}
\end{proof}

@@

\begin{define}
We say an augmentation is \emph{right-augmented} if, when both strands are
(locally) oriented such that they cross the augmentation disk in the same
direction, the crossing is positive/a right-handed half-twist. See Figure
\ref{TODO}
We say an augmentation is \emph{left-augmented} if it is not right-augmented.
\end{define}

@@

By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
obtained by gluing two torihedra with graph $\Gamma_T(L)$ and $\Gamma_B(L)$.
Recall that $\Gamma_T(L)$ is obtained from $\Gamma$ by some slight
modifications, specifically by replacing augmented vertices with bow-ties.
We assign angles to edges of the bow-ties as in TODO figure,
and leave untouched edges with the same assignment of $\pi/2$;
we do the same for $\Gamma_B(L)$.

@@

@@

\begin{proof}
For each directed edge $\vec{e} \in \vec{E}$,
construct the isosceles triangle $T_{\vec{e}}$
with equal sides of length $r_{f_{\vec{e}}}$ and
angle $2\tilde{\vphi}_{\vec{e}}$ subtended between them,
where $\tilde{\vphi}_{\vec{e}} = \vphi_{\vec{e}}$
if $\vphi_{\vec{e}}$ if it is acute,
and = $\pi - \vphi_{\vec{e}}$ otherwise.
(TODO draw figure?)

>>>>

\newcommand{\thmref}[1]{Theorem \ref{#1}}
\newcommand{\prpref}[1]{Proposition \ref{#1}}
\newcommand{\lemref}[1]{Lemma \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\comment}[1]{}

@@

The proof is essentially given in \figref{f:ideal_pyramid_arg} below

\begin{figure}
\label{f:ideal_pyramid_arg}
\includegraphics[height=8cm]{more_pictures/angle_split.png}
\end{figure}
Suppose the edges are labelled $e_i$,
which goes between vertices $v_i$ and $v_{i+1}$,
and suppose $e_i$ is assigned dihedral angle $\alpha_i$.
Let $e'$ be a new edge addeed to the base face of $P_n$
such that it separates the base face into a triangle and
an $(n-1)$-gon;
suppose the sides of the triangle are
$e_i, e_{i+1}$, and $e'$.
The new face corresponding to $e'$ separates $P_n$ into
an ideal tetrahedron $T$ and an ideal pyramid $P_{n-1}$.
We assign the dihedral angle of $\pi - \alpha_i - \alpha_{i+1}$
to $e'$ in $T$, and assign $\alpha_i + \alpha_{i+1}$ to $e'$ in $P_{n-1}$.
Clearly the condition that the sum of dihedral angles are satisfied
in $T$ and $P_{n-1}$.
It remains to check that the dihedral angles assigned to the vertical edges
are correct.
For the vertical edge associated $v_j$ for $j \neq i, i+2$,
there is nothing to check;
for $j = i$, the dihedral angles are
$\pi - \alpha_i - (\pi - \alpha_i - \alpha_{i-1})$
in $T$ and $\pi - \alpha_{i-1} - (\alpha_i + \alpha_{i+1})$ in $P_{n-1}$,
which sum to $\pi - \alpha_i - \alpha_{i+1}$;
it is similar for $j = i+2$.

@@

\begin{define}
We say an augmentation is \emph{right-augmented} if, when both strands are
(locally) oriented such that they cross the augmentation disk in the same
direction, the crossing is positive/a right-handed half-twist.
See \figref{right_left_aug.png}.
We say an augmentation is \emph{left-augmented} if it is not right-augmented.
\begin{figure}
\label{f:right_left_aug}
\includegraphics{more_pictures/right_left_aug.png}
\end{figure}
\end{define}

@@

By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
obtained by gluing two torihedra with graph $\Gamma_T(L)$ and $\Gamma_B(L)$.
Recall that $\Gamma_T(L)$ is obtained from $\Gamma$ by some slight
modifications, specifically by replacing augmented vertices with bow-ties.
We assign angles to edges of the bow-ties as in
\figref{f:bowtie_angles},
and leave untouched edges with the same assignment of $\pi/2$;
we do the same for $\Gamma_B(L)$.

\begin{figure}
\label{f:bowtie_angles}
\includegraphics{more_pictures/horizontal_bowtie.png}
\end{figure}

@@

See \figref{f:adding_edges}

\begin{figure}
\label{f:adding_edges}
\includegraphics[width=5cm]{more_pictures/one_edge.png}
\includegraphics[width=5cm]{more_pictures/two_edge.png}
\includegraphics[width=5cm]{more_pictures/two_edge_many.png}
\end{figure}

@@

\begin{proof}
For each directed edge $\vec{e} \in \vec{E}$,
construct the isosceles triangle $T_{\vec{e}}$
with equal sides of length $r_{f_{\vec{e}}}$ and
angle $2\tilde{\vphi}_{\vec{e}}$ subtended between them,
where $\tilde{\vphi}_{\vec{e}} = \vphi_{\vec{e}}$
if $\vphi_{\vec{e}}$ if it is acute,
and = $\pi - \vphi_{\vec{e}}$ otherwise.

\begin{figure}
\includegraphics[width=8cm]{more_pictures/kite.png}
\end{figure}
\begin{figure}
\includegraphics[width=5cm]{more_pictures/positive_angle.png}
\includegraphics[width=5cm]{more_pictures/negative_angle.png}
\end{figure}
